### 2024-11-12 paper/5-eval.tex
Trim

\red{TODO: Change to array} \\
\red{TODO: Change naming for $c$}
\begin{align}
  &c^* \vdash call(\$brAndReturning); ~ \wasm ~ (\seq{c}, ~ k)
  \label{eq:resolve-1} \\
  &\leadsto c^* \vdash \epsilon; ~ \algo ~ ([ ~ \pushctxi, ~ \enteri ~ ], ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k))
  \label{eq:resolve-2} \\
  &\leadsto Frame, ~ c^* \vdash \epsilon; ~ \algo ~ ([ ~ \enteri ~ ], ~ [ ~ Frame ~ ], ~ \wasm ~ (\seq{c}, ~ k))
  \label{eq:resolve-3} \\
  &\leadsto Label(\epsilon), ~ Frame, ~ c^* \vdash (br ~ \epsilon), ~ (unreachable), ~ (exiting), ~ (returning); \\
  &\quad\quad \wasm ~ ([ ~ Label(\epsilon), ~ Frame ~ ], ~ \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k)))
  \label{eq:resolve-4} \\
  &\leadsto Label(\epsilon), ~ Frame, ~ c^* \vdash (unreachable), ~ (exiting), ~ (returning); \\
  &\quad\quad \algo ~ ([ ~ \popctxi, ~ \executeseqi ~ ], ~ \epsilon, ~ \wasm ~ ([ ~ Label(\epsilon), ~ Frame ~ ], ~ \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k))))
  \label{eq:resolve-5} \\
  &\leadsto Frame, ~ c^* \vdash (returning); ~
    \algo ~ ([ ~ \executeseqi ~ ], ~ \epsilon, ~ \wasm ~ ([ ~ Frame ~ ], ~ \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k))))
  \label{eq:resolve-6} \\
  &\leadsto Frame, ~ c^* \vdash (returning); ~
    \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ ([ ~ Frame ~ ], ~ \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k))))
  \label{eq:resolve-7} \\
  &\leadsto Frame, ~ c^* \vdash (returning); ~ \wasm ~ ([ ~ Frame ~ ], ~ \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k)))
  \label{eq:resolve-8} \\
  &\leadsto Frame, ~ c^* \vdash \epsilon; ~
    \algo ~ ([ ~ \popctxi ~ ], ~ \epsilon, ~ \wasm ~ (\epsilon, ~ \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k))))
  \label{eq:resolve-9} \\
  &\leadsto c^* \vdash \epsilon; ~
    \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\epsilon, ~ \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k))))
  \label{eq:resolve-10} \\
  &\leadsto c^* \vdash \epsilon; ~ \wasm ~ (\epsilon, ~ \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k)))
  \label{eq:resolve-11} \\
  &\leadsto c^* \vdash \epsilon; ~ \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k))
  \label{eq:resolve-12} \\
  &\leadsto c^* \vdash \epsilon; ~ \wasm ~ (\seq{c}, ~ k)
  \label{eq:resolve-13}
\end{align}

>>>>

\red{TODO: Change to array} \\
\red{TODO: Change naming for $c$}
\begin{align}
  &c^* \vdash call(\$brAndReturning); ~ \wasm ~ (\seq{c}, ~ k)
  \label{eq:resolve-1} \\
  &\leadsto c^* \vdash \epsilon; ~ \algo ~ ([ ~ \pushctxi, ~ \enteri ~ ], ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k))
  \label{eq:resolve-2} \\
  &\leadsto Frame, ~ c^* \vdash \epsilon; ~ \algo ~ ([ ~ \enteri ~ ], ~ [ ~ Frame ~ ], ~ \wasm ~ (\seq{c}, ~ k))
  \label{eq:resolve-3} \\
  &\leadsto Label(\epsilon), ~ Frame, ~ c^* \vdash (br ~ \epsilon), ~ (unreachable), ~ (exiting), ~ (returning); \\
  &\quad\quad \wasm ~ ([ ~ Label(\epsilon), ~ Frame ~ ], ~ \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k)))
  \label{eq:resolve-4} \\
  &\leadsto Label(\epsilon), ~ Frame, ~ c^* \vdash (unreachable), ~ (exiting), ~ (returning); \\
  &\quad\quad \algo ~ ([ ~ \popctxi, ~ \executei ~ ], ~ \epsilon, ~ \wasm ~ ([ ~ Label(\epsilon), ~ Frame ~ ], ~ \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k))))
  \label{eq:resolve-5} \\
  &\leadsto Frame, ~ c^* \vdash (returning); ~
    \algo ~ ([ ~ \executei ~ ], ~ \epsilon, ~ \wasm ~ ([ ~ Frame ~ ], ~ \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k))))
  \label{eq:resolve-6} \\
  &\leadsto Frame, ~ c^* \vdash (returning); ~
    \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ ([ ~ Frame ~ ], ~ \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k))))
  \label{eq:resolve-7} \\
  &\leadsto Frame, ~ c^* \vdash (returning); ~ \wasm ~ ([ ~ Frame ~ ], ~ \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k)))
  \label{eq:resolve-8} \\
  &\leadsto Frame, ~ c^* \vdash \epsilon; ~
    \algo ~ ([ ~ \popctxi ~ ], ~ \epsilon, ~ \wasm ~ (\epsilon, ~ \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k))))
  \label{eq:resolve-9} \\
  &\leadsto c^* \vdash \epsilon; ~
    \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\epsilon, ~ \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k))))
  \label{eq:resolve-10} \\
  &\leadsto c^* \vdash \epsilon; ~ \wasm ~ (\epsilon, ~ \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k)))
  \label{eq:resolve-11} \\
  &\leadsto c^* \vdash \epsilon; ~ \algo ~ (\epsilon, ~ \epsilon, ~ \wasm ~ (\seq{c}, ~ k))
  \label{eq:resolve-12} \\
  &\leadsto c^* \vdash \epsilon; ~ \wasm ~ (\seq{c}, ~ k)
  \label{eq:resolve-13}
\end{align}
